---
title: "Group 10 - Project Proposal"
author: "Yifan Chen, Shumeng Fang, Rui Zhang, Shixin Zhang"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This proposal aims to predict total precipitation, maximum temperature, and minimum temperature by comparing multiple statistical methods. 

#### Read Data
```{r }
cental_west <- read.csv('Data/central_west.csv')
north <- read.csv('Data/north.csv')
northeast <- read.csv('Data/northeast.csv')
south <- read.csv('Data/south.csv')
southeast <- read.csv('Data/southeast.csv')

```
#### Data Description

The dataset contains 27 variables, and here we only present representative variables to illustrate the data format.


| Variable          | Type       | Description                                                                 |
|-------------------|    :------------:|--------------------------------------|
|Precipitation|dbl|Amount of precipitation in millimetres (last hour)|
|Pressure|dbl|Atmospheric pressure at station level (mb)|
|AirTemp|dbl|Air temperature (instant) (°c)|
|Humid|int|Relative humid (% instant)|
|Latitude|dbl



#### Methods


1.Data Pre-processing

  a. Data Imputation: Replace missing categorical values with the mode (most frequent value) of the observed values for that variable.
  b. One-Hot Encoding for non-numeric variable.

2.Statistical Methods

  a. Linear Model: Use OLS to predict the total precipitation, max temperature and min temperature.
  b. Lasso Regression: Enhance feature selection when doing prediction.
  c. Random Forest: Improve prediction accuracy by constructing multiple decision trees and combining their predictions.
  d. SARIMA: Use time series methods by capturing seasonal trend to forecast temperature.

3.Parallel Computing

  a. Since the dataset is already divided into five geographic subsets, we propose a parallel computing approach to build predictive models tailored to each region and find out the optimal models for each one.
  b. When doing prediction, a new data point will first be assigned to its respective region, then the region-specific model will be applied for accurate forecasting.

#### GitHub
git clone https://github.com/rzhang534/DSCPproject.git
